FraCaS: Temporal Analysis

### 2020-05-26 paper2020/paper.tex
minor

\paragraph{Montegovian semantics}
\todo{integrate to background}

Our interpretation is cast withing the framework of a largely standard
montegovian semantics \cite{todo}. In brief, sentences are interpreted as
propositions, verbs and noun-phrases as predicates.  We use
type-raising of noun-phrases, to support quantifiers~\cite{PTQ}.

@@

In montegovian semantics, (intransitive) verbs are one-place
predicates; in types, they are functions from entities to propositions
($e \to t$).  Our basic approach is to generalise the interpretation of 
verbs, so that it takes two
additional time parameters, one corresponding with the starting time
of the action and one corresponding to its stopping time ($(time × time × e) \to t$). For example,
if John walked between $t_0$ and $t_1$, we would have:
$walk(john,t_0,t_1)$. From now on we will call an interval of time
points $[t_0,t_1]$ a timespan. Every timespan $[t_0,t_1]$ has the
property $t_0 ≤ t_1$ (it starts no later than it stops). (We are thus
using a simple newtonian model of time, corresponding to a layman
intuition.)

@@

We adjust the montegovian semantics so that the interpretation of
every category (propositions, verb phrases, etc.) takes a
\emph{temporal context} as an additional parameter, serves as a time
reference for the interpretation of all time-dependent semantics
within the phrase.  This context propagates through the compositional
interpretation down to lexical items with atomic representation
(verbs). By default, every interpretation passes the temporal context
down to its components without changing it. However some key elements
will act on it on nontrivial ways, which we proceed to detail below.

@@

The issue is that the quantification introduced by the temporal marker
is outside the negation. For example, the premiss of (038) is
interpreted as ``there exists a time in the past when every delegate
did not finish the report'' --- which is incorrect in this context.
\fracasex{038}{
\item	No delegate finished the report.
\hyp 	Some delegate finished the report on time.
}
%
We stress that such interaction between quantifiers and negation
already occurs without temporal analysis: one must make a difference
between narrow scoping and wide scoping \cite{todo}. Unfortunately,
the montegovian system over which we base our implementaiton does not
support this phenomena. (Indeed the test suite does not appear to
handle this case). We propose that the situation becomes
quantitatively more difficult to handle with the added complication of
time-quantification, but not fundamentally different.
%
A similar issue occurs with group readings, which are interpreted as
conjunctions. Here, the problem is to solve the order of scoping
between this conjunction and time-interval quantifiers.

>>>>

\paragraph{Montagovian semantics}
\todo{integrate to background}

Our interpretation is cast withing the framework of a largely standard
montagovian semantics \cite{todo}. In brief, sentences are interpreted as
propositions, verbs and noun-phrases as predicates.  We use
type-raising of noun-phrases, to support quantifiers~\cite{PTQ}.

@@

In montagovian semantics, (intransitive) verbs are one-place
predicates; in types, they are functions from entities to propositions
($e \to t$).  Our basic approach is to generalise the interpretation of 
verbs, so that it takes two
additional time parameters, one corresponding with the starting time
of the action and one corresponding to its stopping time ($(time × time × e) \to t$). For example,
if John walked between $t_0$ and $t_1$, we would have:
$walk(john,t_0,t_1)$. From now on we will call an interval of time
points $[t_0,t_1]$ a timespan. Every timespan $[t_0,t_1]$ has the
property $t_0 ≤ t_1$ (it starts no later than it stops). (We are thus
using a simple newtonian model of time, corresponding to a layman
intuition.)

@@

We adjust the montagovian semantics so that the interpretation of
every category (propositions, verb phrases, etc.) takes a
\emph{temporal context} as an additional parameter, serves as a time
reference for the interpretation of all time-dependent semantics
within the phrase.  This context propagates through the compositional
interpretation down to lexical items with atomic representation
(verbs). By default, every interpretation passes the temporal context
down to its components without changing it. However some key elements
will act on it on nontrivial ways, which we proceed to detail below.

@@

The issue is that the quantification introduced by the temporal marker
is outside the negation. For example, the premiss of (038) is
interpreted as ``there exists a time in the past when every delegate
did not finish the report'' --- which is incorrect in this context.
\fracasex{038}{
\item	No delegate finished the report.
\hyp 	Some delegate finished the report on time.
}
%
We stress that such interaction between quantifiers and negation
already occurs without temporal analysis: one must make a difference
between narrow scoping and wide scoping \cite{todo}. Unfortunately,
the montagovian system over which we base our implementaiton does not
support this phenomena. (Indeed the test suite does not appear to
handle this case). We propose that the situation becomes
quantitatively more difficult to handle with the added complication of
time-quantification, but not fundamentally different.
%
A similar issue occurs with group readings, which are interpreted as
conjunctions. Here, the problem is to solve the order of scoping
between this conjunction and time-interval quantifiers.
